Bone-Conduction Audio Interface to\\Guide People with Visual Impairments

### 2019-07-15 paper.tex
Fixed clunky sentence in conclusion

In this work, we proposed an audio interface that conveys a target's pan and elevation angles through a spatialised audio tone that adjusts the tone's pitch to convey the elevation in compensate for the shortcomings of bone-conduction headsets in transmitting the elevation component of a spatialised signal.
Results generated from a simple pointing experiment are encouraging and improves performance over purely spatialised signals transmitted via bone-conduction.
Furthermore, the limitations of these headphones were largely negated by conveying the elevation angle of the target by adjusting the tone's pitch, with pan and elevation errors comparable to that from normal over-ear headphones.

>>>>

In this work, we proposed an audio interface that conveys a target's pan and elevation angles through a spatialised audio tone.
To compensate for the shortcomings of bone-conduction headsets and standard HRTFs, the elevation is given by adjusting the tone's pitch.
Results generated from a simple pointing experiment are encouraging and improves performance over purely spatialised signals transmitted via bone-conduction.
Furthermore, the limitations of these headphones were largely negated by conveying the elevation angle of the target by adjusting the tone's pitch, with pan and elevation errors comparable to that from normal over-ear headphones.
